Lifting CDCL to Numerical Domains

### 2016-09-26 domains.tex
domain

\subsection{Conditions for Absract Domains}
An important criterion to support clause learning in 
partial assignments domain is that elements in the 
domain must have complementation property.  Most 
numerical abstract domain does not support 
complementation operator.  Similar to the interval 
domain, octagons does not have complementation 
property, but the decomposition of octagons into 
half spaces are complementable.

APRON library is specialized for the abstract interpretation 
framework which does not require complementation 
operator.  So, we implement our own template-based 
octagon domain which supports complementation operator.

The octagon in example can be written as a conjunction of:
\[(x>=-2) \land (x<=1) \land (y>=-1) \land (y<=2) \land (x+y<=2) \land (x-y<=1) \land (y-x<=3) \land (-x-y<=2)\]

>>>>

\subsection{Conditions for Absract Domains}
One of the requirements for a clause learning SAT solver 
is that each element of the partial assignments domain 
needs to have a decomposition into precisely complementable 
elements.  This property of the underlying domain helps 
guiding the search away from the conflicting region of the search 
space.

Thus, clause learning SAT solvers requires a weak complementation property
of the abstraction.  However, numerical abstract domain,  such as 
intervals and octagons are intersections of complementable half-spaces. 
APRON library is specialized for the abstract interpretation 
framework which does not require complementation 
operator.  To this end, we implement our own template-based 
octagon domain which supports complementation operator.

For example, the octagon in example can be written as a conjunction of:
\[(x>=-2) \land (x<=1) \land (y>=-1) \land (y<=2) \land (x+y<=2) \land (x-y<=1) \land (y-x<=3) \land (-x-y<=2)\]

### 2016-09-26 paper.tex
domain

\author{Rajdeep Mukherjee Peter Schrammel   Daniel Kroening}

@@

%===============================================================================
\begin{abstract}
%===============================================================================
%
The conflict driven clause learning algorithm can be seen as an 
alternation between over-approximate deduction with boolean 
constraint propagation, and under-approximate abduction, with 
conflict analysis.  {\em Abstract Conflict Driven Clause Learning} 
(ACDCL) is a novel program analysis that embeds an abstract domain 
inside the Conflict Driven Clause Learning (CDCL) algorithm. From 
decision procedure perspective, ACDCL is a SAT solver for program 
analysis constraints and is a strict generalisation of propositional CDCL 
solvers. From Abstract Interpretation point of view, ACDCL can be 
viewed as an abstract interpreter that uses decision and learning to 
increase the precision of abstract transformers.  In this paper, we 
instantiate ACDCL with different relational and non-relational numerical 
abstract domains and evaluate the performance of our program analyzer
with program verifiers that uses propositional-level solvers.  Experimental 
evidence on a set of \rmcmt{N} benchmarks shows significant drop in number 
of decisions and backjumping iterations in addition to stronger 
deductions and learned clause aided by the richer abstract domains.
%
\end{abstract}
%===============================================================================
\input{introduction}
%===============================================================================

>>>>

\author{Rajdeep Mukherjee\inst{1} Peter Schrammel   Daniel Kroening}

@@

%===============================================================================
\begin{abstract}
%===============================================================================
%
The Conflict Driven Clause Learning (CDCL) algorithm can be seen as an 
alternation between over-approximate deduction with boolean 
constraint propagation, and under-approximate abduction, with 
conflict analysis.  {\em Abstract Conflict Driven Clause Learning} 
(ACDCL) is a novel program analysis that embeds an abstract domain 
inside the CDCL algorithm. From decision procedure perspective, 
ACDCL is a SAT solver for program analysis constraints and is a 
strict generalisation of propositional CDCL solvers. From Abstract 
Interpretation point of view, ACDCL can be viewed as an abstract 
interpreter that uses decision and learning to increase the precision 
of abstract transformers.  In this paper, we instantiate ACDCL with 
a relational and a non-relational numerical abstract domain and 
evaluate the performance of our analyzer with program verifiers that 
uses propositional-level solvers.  Experimental evidence on a set of 
\rmcmt{N} benchmarks \rmcmt{drawn from X} shows significant reduction 
in the number of decisions and backjumping iterations along with stronger 
deductions and learned clause aided by the richer abstract domains.
%
\end{abstract}
%===============================================================================
\input{introduction}
%===============================================================================
